Capturing the shape of our experiences and how we remember them

### 2018-08-16 paper/main.tex
..
commenting out brain methods

\title{Capturing the geometric structure of our experiences and how we remember them}
% \title{The fundamental shape of naturalistic experiences is preserved in episodic memory}
% \title{Memory dynamics for naturalistic experiences}
\author{Andrew C. Heusser \& Jeremy R. Manning}
% \affiliation{Dartmouth College}

@@

 \subsection{fMRI analyses}
 Seventeen participants watched the first 50 minutes of Episode 1 of BBC's Sherlock. The video was split into two parts of approximately equal length (946 and 1030 TRs). All data were preprocessed and transformed to 3mm MNI space as described in the paper. Data were zscored across time at every voxel. 6mm smoothing was applied.
 Files are cropped so that all video-viewing data are aligned across participants, and all recall data are aligned to the scene timestamps below. The cropping includes a constant 3-TR (4.5 sec) shift to correct for hemodynamic lag.

 \subsubsection{Searchlight analysis}
 Our multivariate analyses were designed to capture brain regions whose timepoint-by-timepoint correlational structure mirrors the correlational structure of the participant-specific recall topic models during video viewing. To correct for non-linearities between the viewing time and recall time, for each participant we used DTW to temporally align the matrices. The algorithm recovers a path of coordinates that would bring the video and recall model in maximal temporal alignment. We used this path to warp the fMRI data and the recall model into temporal alignment (separately for each participant). Then, we conducted a searchlight analysis (5x5x5 voxel cube) where for each cube, we correlated the model timepoint-by-timepoint correlation matrix with the neural correlation matrix. To aggregate across participants, we Fisher's z-transformed the correlations and then averaged.  To assess significance, we recomputed this group analysis 100 times, but randomly phase shifted the model (by \# of timepoints - 1) by the same amount for each participant but different amounts for each permutation to build a null distribution of correlation values. Finally, we thresholded the group averaged correlation maps where the `real' correlation value for a given voxel exceeded the 95th percentile of the null distribution.

>>>>

\title{Capturing the shape of our experiences and how we remember them}
% \title{The fundamental shape of naturalistic experiences is preserved in episodic memory}
% \title{Memory dynamics for naturalistic experiences}
\author{Andrew C. Heusser \& Jeremy R. Manning}
% \affiliation{Dartmouth College}

@@

 % \subsection{fMRI analyses}
 % Seventeen participants watched the first 50 minutes of Episode 1 of BBC's Sherlock. The video was split into two parts of approximately equal length (946 and 1030 TRs). All data were preprocessed and transformed to 3mm MNI space as described in the paper. Data were zscored across time at every voxel. 6mm smoothing was applied.
 % Files are cropped so that all video-viewing data are aligned across participants, and all recall data are aligned to the scene timestamps below. The cropping includes a constant 3-TR (4.5 sec) shift to correct for hemodynamic lag.
 %
 % \subsubsection{Searchlight analysis}
 % Our multivariate analyses were designed to capture brain regions whose timepoint-by-timepoint correlational structure mirrors the correlational structure of the participant-specific recall topic models during video viewing. To correct for non-linearities between the viewing time and recall time, for each participant we used DTW to temporally align the matrices. The algorithm recovers a path of coordinates that would bring the video and recall model in maximal temporal alignment. We used this path to warp the fMRI data and the recall model into temporal alignment (separately for each participant). Then, we conducted a searchlight analysis (5x5x5 voxel cube) where for each cube, we correlated the model timepoint-by-timepoint correlation matrix with the neural correlation matrix. To aggregate across participants, we Fisher's z-transformed the correlations and then averaged.  To assess significance, we recomputed this group analysis 100 times, but randomly phase shifted the model (by \# of timepoints - 1) by the same amount for each participant but different amounts for each permutation to build a null distribution of correlation values. Finally, we thresholded the group averaged correlation maps where the `real' correlation value for a given voxel exceeded the 95th percentile of the null distribution.
